---
title: "Quick introduction to the workflow"
author: "Kuo-Lin Tang"
date: "13/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Topic Modeling Workflow
A topic consists of a collection of words.

Here, we are focusing on Latent Dirichlet Allocation. LDA takes a document-term matrix (DTM) as an input. LDA returns two matrices: Document-Topic matrix and Topic-Term matrix

## Useful packages
```{r}
library(tidyverse)
library(tidytext)
```

# Counting words
To fit a topic model, we must prepare a document-term matrix (contains counts of word occurences in documents) using **tidytext** and **tidyverse**.


## Tokenisation
unnest_tokens(data, input=text, output=word, format="text", tokens="word", drop=TRUE, to_lower=TRUE)

### Example
```{r}
book = data.frame(chapter = c(1, 2), text = c("It is what it is", "What goes around comes around."))

book %>%
  unnest_tokens(input = text, 
                output = word,
                token = "words",
                format = "text",
                drop = T,
                to_lower = T)
```


## Count()
Count frequency of words

### Example
```{r}
book %>%
  unnest_tokens(input = text, 
                output = word,
                token = "words",
                format = "text",
                drop = T,
                to_lower = T) %>%
  count(chapter, word)
```

### Get the most frequent words of the whole book
```{r}
book %>%
  unnest_tokens(input = text, 
                output = word,
                token = "words",
                format = "text",
                drop = T,
                to_lower = T) %>%
  count(chapter, word) %>%
  top_n(1, n)
```

### Get the most frequent words of each chapter
```{r}
book %>%
  unnest_tokens(input = text, 
                output = word,
                token = "words",
                format = "text",
                drop = T,
                to_lower = T) %>%
  count(chapter, word) %>%
  group_by(chapter) %>%
  top_n(1, n)
```


## Transform a count() object into a Document-Term matrix
Use cast_dtm(document = DOCUMENT_ID, term = WORD, value = COUNT)
```{r}
dtm = book %>%
  unnest_tokens(input = text, 
                output = word,
                token = "words",
                format = "text",
                drop = T,
                to_lower = T) %>%
  count(chapter, word) %>%
  cast_dtm(document = chapter, term = word, value = n)
```

### Check the DTM
```{r}
as.matrix(dtm)
```



# The first Latent Dirichlet Allocation (LDA) model
```{r}
library(topicmodels)

LDA_model1 = LDA(x = dtm, 
                 k = 2, 
                 method = "Gibbs", 
                 control = list(alpha = 1, 
                                delta = 0.1, 
                                seed = 42))
```


# Display frequency with ggplot
## Display two kinds of data
1. Word counts (obtained before topic modeling)
2. Probabilities of topics and words (obtained after topic modeling)

由於ggplot的輸入只能接受tidy format的東西，例如tibbles、dataframes等等。而透過count()函數得到的word counts已經是tidy format了，因此可以直接用ggplot畫出。然而，LDA model中的probabilities of topics and words (beta and gamma)並不是tidy format，因此要用tidy()函數將beta、gamma物件轉換成tidy format data


**beta**: 記錄著各個term屬於某一個topic的機率 (一個topic-term matrix)
**gamma**: 記錄著每個document中各topic佔有的比例 (一個document-topic matrix) (總和是1)

因此，LDA就是將一個document-term matrix轉換成一個topic-term matrix和一個document-topic matrix


## Tidy() 函數
tidy(lda_model, matrix = "beta") 代表取出lda_model中的beta矩陣
tidy(lda_model, matrix = "gamma") 代表取出lda_model中的gamma矩陣

### Visualising
#### Stacked columns chart
```{r}
tidy(LDA_model1, matrix = "gamma") %>%
  ggplot(aes(x = document, y = gamma)) +
  geom_col(aes(fill = as.factor(topic)))
```
由於一個文件的所有topics的比例總和為1，因此很適合用stacked columns chart


#### Dodged columns chart
```{r}
tidy(LDA_model1, matrix = "beta") %>%
  ggplot(aes(x = term, y = beta)) +
  geom_col(aes(fill = as.factor(topic)),
           position = position_dodge())
```
beta為每一個字詞屬於各topic的機率，多用dodged columns chart來視覺化

由於每個詞的長度不同，因此當corpus中有很多字詞時，有可能會在圖中重疊。因此可以將每個字詞都變成直的
```{r}
tidy(LDA_model1, matrix = "beta") %>%
  mutate(topic = as.factor(topic)) %>%
  ggplot(aes(x = term, y = beta)) +
  geom_col(aes(fill = topic),
           position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 90))
```